How Optimal is Word-Referent Identification Under Multimodal Uncertainty?

### 2019-03-16 Writeup/ms.tex
revisions

Although the paradigm is within-subjects, we did not have enough
statistical power to fit a different model for each individual
participant. Instead, models were constructed with data collapsed across
all participants. The fit was done with a nonlinear least squares
regression using the NLS package in R (Bates \& Watts, 1988). We
computed the values of the parameters, as well as their 95\% confidence
intervals, through non-parametric bootstrap (using 10000 iterations).

@@

Average categorization judgments and best fits are shown in
Figure~\ref{fig:unimodal}. The categorization function of the auditory
condition was slightly steeper than that of the visual condition,
meaning that participants perceived the sound tokens slightly more
categorically and with higher certainty than they did with the visual
tokens. For the auditory modality, we obtained the following values:
\(b_A=\) -0.20 {[}0.02, -0.38{]} and \(\sigma^2_A=\) 2.04 {[}1.66,
2.53{]}. For the visual modality, we obtained \(b_V=\) -0.12 {[}0.06,
-0.28{]} and \(\sigma^2_V=\) 3.33 {[}2.83, 3.92{]}.

@@

Figure~\ref{fig:bimodal} compares the predictions of the normative
models against human responses. Remember that the normative models use
variance estimates from the unimodal conditions (where people see input
from only one modality) to predict data in the bimodal condition (where
people see input from both modalities). Each point represents data form
a particular audio-visual matching (e.g., the visual token \(v\) whose
distance from the target \(v_t\) is \(|v-v_t|=3\), matched with the
auditory token \(a\) whose distance from the target \(a_t\) is
\(|a-a_t|=2\)). The visual, auditory and optimal model explained,
respectively, 30\%, 67\%, and 89\% of total variance in mean responses.

@@

In the descriptive model, all parameters are fit to human responses in
the bimodal condition. We found \(b=\) -0.34 {[}-0.28, -0.39{]},
\(\sigma^2_{Ab}=\) 4.96 {[}4.58, 5.40{]} and \(\sigma^2_{Vb}=\) 7.06
{[}6.40, 7.84{]}. Note that the variance of both the auditory and visual
modalities increased compared to the unimodal conditions.

\noindent The descriptive model explained 95\% of total variance.
However, since the descriptive model was fit to the same data, there is
a risk that this high correlation is due to overfitting. To examine this
possibility, we cross-validated the model using half the responses to
predict the other half (averaging across 10 random partitions). The
predictive power of the model remained very high (\(r^2\)=0.93).

\begin{figure}[!h]
\includegraphics[width=\textwidth]{ms_files/figure-latex/bimodal-1} \caption{Human responses vs. Models' predictions in the bimodal condition across the three experiments. Each point represents data form a particular audio-visual matching. Shape represents auditory distance from the target, and color represents visual distance from the target. Thus, each point is characterized by both  shape and color.}\label{fig:bimodal}
\end{figure}

\paragraph{Cue combination and Modality
preference}\label{cue-combination-and-modality-preference}

We next analyzed if cue combination was performed in an optimal way, or
if there was a systematic preference for one modality when making
decisions in the bimodal condition. As explained above, modality
preference can be characterized formally as a deviation from the
decision threshold predicted by the optimal model. Figure~\ref{fig:bias}
(top) shows both the decision threshold derived from the descriptive
model (in black) and the decision threshold predicted by the optimal
model (in red). The deviation from optimality is compared to two
hypothetical cases of modality preference (dotted lines). We found that
the descriptive and optimal decision thresholds were almost identical.
Indeed, non-parametric resampling of the data showed no evidence of a
deviation from the optimal prediction (Figure~\ref{fig:bias}, bottom).

@@

Overall, we found that the optimal model explained much of the variance
in the mean judgments, and largely more than what can be explained with
the auditory or the visual models alone. Moreover, the high value of the
coefficient of determination in the optimal model (\(r^2\)=0.89)
suggests that the population was near-optimal. However, we see in
Figure~\ref{fig:bimodal} that the mean responses deviated systematically
from the optimal prediction in that they were slightly pulled toward
chance (i.e., the probability 0.5). This fact is due to the increase in
the value of the variance associated with each modality. Note however
that, despite this increase in randomness, our analysis of modality
preference showed that the relative values of these variances were not
different (Figure~\ref{fig:bias}), meaning that there was no evidence
for a modality preference. Thus, 1) There was a simultaneous increase in
the values of the auditory and visual variances in the bimodal condition
compared to the unimodal condition, meaning that the bimodal input lead
to an increase in response randomness, and 2) this increased randomness
did not affect the relative weighting of both modalities, i.e., the
participants was weighting modalities according to the relative
reliability predicted by the optimal model. This situation corresponds
to the first case of sub-optimality described in
Figure~\ref{fig:subOptim}.

\begin{figure}[!h]
\includegraphics[width=\textwidth]{ms_files/figure-latex/individual-1} \caption{Distributions of individual values of the visual variance relative to the auditory variance in Experiment 1. Light color represents the real individual distribution, and dark color represents the simulated individual distribution sampled from the descriptive model.}\label{fig:individual}
\end{figure}

As we noted earlier, we did not have enough statistical power to fit a
different model for each individual participant. Instead, we fit one
model using the data aggregated across all participants. This analysis
is informative of behavior at the population level, only. However,
optimality at the population level could be misleading. Imagine, for
instance, that in the bimodal condition half the participants relied
exclusively on the visual modality, whereas the other half relied
exclusively on the auditory modality. This case could still lead to an
aggregate behavior which appears optimal, but this optimality would be
spurious. This, in the experiemnt below, we test the cue integration
strategy at the individual level. To this end, we increase the
statistical power by extending the length of the experiment, allowing us
to collect the number of datapoints necessary to fit the models for each
participant.

\section{Experiment 1 bis}\label{experiment-1-bis}

@@

@@

We fit both population-level models to the aggregated data (as in
Experiment 1), and individual models to data from each participant. For
the populaton-level models, the results (shown in
Figure~\ref{fig:unimodal}) replicated the results obtained in Experiment
1. As for the individual-level analysis, the models showed there to be
between-subject variability as seen in the paramters's distribution in
Figure XX.

\subsubsection{Bimodal condition and Cue combination
models}\label{bimodal-condition-and-cue-combination-models}

We first generated poupulation-level normative and descriptive models.
As shown in Figure~\ref{fig:bimodal}, the predicted patterns of these
models mirrored closely the results obtained in Experiment 1. In
addition, the optimality analysis (i.e., done through comparing the
optimal and descriptive models) shows that the fitted mean decision
threshold was indisguisable form the optimal threshold, thus replicating
the results of Experiment 1 (Figure~\ref{fig:bias} shows that).

At the individual level, we computed the distribution of optimal
weighing relative to the fitted (i.e., descriptive) weighing and we show
this distribution in Figure XX. The distribution centers around the
optimal prediction (i.e., 1) with a median value of XX {[}XX,XX{]}. The
variance of the distribution indicates that, while most participants
were near optimal in their cue combination, part of the participant
tended to rely predominantly on the auditory modality and another part
tended to rely predominantly on the visual modality.

@@

In Experiment 1 and Experiment 1 bis, we tested word recognition when
there was multimodal uncertainty in terms of category membership and
inherent perceptual noise, only. In real life, however, both sound and
visual tokens can undergo distortions due to noisy factors in the
environment (e.g., car noise in the background, blurry vision in a foggy
weather). In Experiment 2 and 3, we explore this additional level of
uncertainty.

\subsection{Results and analysis}\label{results-and-analysis-2}

\subsubsection{Unimodal conditions}\label{unimodal-conditions-3}

We fit a model for each modality. For the auditory modality, our
parameter estimates were \(b_A=\) -0.18 {[}-0.05, -0.30{]} and
\(\sigma^2_A+\sigma^2_N=\) 4.70 {[}4.03, 5.55{]}. For the visual
modality, we found \(b_V=\) -0.24 {[}-0.10, -0.36{]} and \(\sigma^2_V=\)
3.93 {[}3.43, 4.55{]}. Figure~\ref{fig:unimodal} shows responses in the
unimodal conditions as well as the corresponding best fits. The visual
data is a replication of the visual data in Experiment 1. As for the
auditory data, in contrast to Experiment 1, responses were flatter,
showing more uncertainty.

Figure~\ref{fig:bimodal} compares the predictions of the visual,
auditory and optimal models to human responses. These normative models
explained, respectively, 77\%, 21\%, and 91\% of total variance in mean
judgements. Note that, in contrast to Experiment 1, the visual model
explained more variance than the auditory model did.

\paragraph{Descriptive model}\label{descriptive-model-1}

We estimated \(b=\) -0.38 {[}-0.33, -0.42{]},
\(\sigma^2_{Ab}+\sigma^2_{Nb}=\) 9.84 {[}8.75, 11.27{]}, and
\(\sigma^2_{Vb}=\) 5.21 {[}4.84, 5.64{]}. The fit explained 0.97\% of
total variance. Cross-validation using half the responses to predict the
other half yielded \(r^2 =\) 0.96.

We found, similar to Experiment 1, that the population was generally
near optimal (\(r^2 =\) 0.91), and that the optimal model explained more
variance than the auditory or the visual models alone. We also found a
similar discrepancy from the optimal model as precision dropped for both
the auditory and the visual modalities. As for the weighting scheme used
by participants, contrary to Experiment 1 where modalities were weighted
according to their relative reliability, we found in this experiment
that the visual modality had a greater weight than what was expected
from its relative reliability. This situation corresponds to the second
case of sub-optimality described in Figure~\ref{fig:subOptim}.

We were also interested in whether noise in the auditory modality lead
more participants to rely exclusively on the visual modality at the
individual level. Using the same cut-off as in Experiment 1 (a factor of
10), the percentage of participants who relied exclusively on either
modality was 34.41\%, which is much higher than the percentage obtained
in Experiment 1 (21.25\%). Moreover, the subset of participants relying
exclusively on the visual modality (compared to those who relied
exclusively on the auditory modality) increased from 29.41\% in
Experiment 1 to 68.75\% in Experiment 2, indicating that noise in the
auditory modality prompted more participants to rely exclusively and
disproportionately on the visual modality (see Table
\ref{tab:exclusive}).

\subsection{Results and analysis}\label{results-and-analysis-3}

\subsubsection{Unimodal conditions}\label{unimodal-conditions-4}

For the auditory modality, our parameter estimates were \(b_A=\) -0.24
{[}-0.04, -0.42{]} and \(\sigma^2_A=\) 1.94 {[}1.61, 2.33{]}. For the
visual modality, we found \(b_V=\) 0.11 {[}0.27, -0.03{]} and
\(\sigma^2_V+\sigma^2_N=\) 13.00 {[}9.92, 18.94{]}.
Figure~\ref{fig:unimodal} shows responses in the unimodal conditions as
well as the corresponding fits. The auditory data is a replication of
the auditory data in Experiment 1. As for the visual data, we found
that, in contrast to Experiment 1 and 2, responses were flatter, showing
much more uncertainty.

\paragraph{Normative models}\label{normative-models-2}

Figure~\ref{fig:bimodal} compares the predictions of the visual,
auditory and optimal models to human responses. These normative models
explained, respectively, 1\%, 98\%, and 97\% of total variance in the
mean judgements.

\paragraph{Descriptive model}\label{descriptive-model-2}

We estimated \(b=\) -0.35 {[}-0.29, -0.40{]}, \(\sigma^2_{Ab}=\) 3.00
{[}2.75, 3.25{]}, and \(\sigma^2_{Vb}+\sigma^2_{Nb}=\) 39.42 {[}25.06,
98.96{]}. The fit explained 97\% of total variance. Cross-validation
using half the responses to predict the other half yielded \(r^2=\)
0.96.

\paragraph{Modality preferences}\label{modality-preferences-1}

We found that the optimal model accounted for almost all the variance
(\(r^2 =\) 0.97). However, whereas in previous experiments the optimal
model explained more variance than the auditory or the visual models,
here the auditory model explained at least as much variance (\(r^2 =\)
0.98). Thus, though participants were still sensitive to variation in
the noisy visual data in the unimodal condition, they tended to ignore
this information in the bimodal condition, and relied almost exclusively
on the non-noisy auditory modality. The reason why we saw this (floor)
effect when we added noise to the visual modality (Experiment 3), and
not when we added noise to the auditory modality (Experiment 2), is the
fact that our visual stimuli were originally perceived less
categorically and with less certainty than the auditory stimuli. This
fact made it more likely for the visual categorization function to
become flat and uninformative after a few drops in precision due to
noise on the one had, and to the additional randomness induced by the
bimodal presentation on the other hand.

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:exclusive}The percentage of participants who relied exclusively on either the visual modality or the auditory modality, using a factor of 10 as a cut-off (e.g., we consider that a participant relied exclusively on the visual modality when their auditory variance is a at least 10 times larger than their visual variance). We show the percentage compared to the total number of participants in each Experiment (`of Total'). From this subset of participants, we show the percentage of those who relied on the  auditory modality (`Auditory'), and the percentage of those who relied on the visual  modality (Visual').}
\begin{tabular}{llll}
\toprule
Experiment & \multicolumn{1}{c}{ofTotal} & \multicolumn{1}{c}{Auditory} & \multicolumn{1}{c}{Visual}\\
\midrule
Exp1 & 21.25 & 70.59 & 29.41\\
Exp2 & 34.41 & 31.25 & 68.75\\
Exp3 & 38.64 & 94.12 & 5.88\\
\bottomrule
\end{tabular}
\end{threeparttable}
\end{center}
\end{table}

The percentage of participants who relied exclusively on either the
visual modality or the auditory modality was 38.64\%, which is closer to
the percentage of Experiment 2, except that now almost all of them
relied on the auditory modality (94.12\%). For ease of comparison, Table
\ref{tab:exclusive} provides a summary of the numbers across the three
experiments.

@@

In all of our experiments, at the highest level, we found generally
optimal behavior. Quantitatively speaking, the optimal model accounted,
respectively, for 89\%, 91\%, and 97\% of the variance in mean
responses. When compared to the predictions of the visual or the
auditory models, participants generally relied on both modalities to
make their decisions in the bimodal condition. Indeed, in Experiment 1
and 2, the optimal model accounted for more variance in mean responses
than the auditory or the visual models did. In Experiment 3,
participants appeared to rely on one modality, but this was likely a
floor effect, due to the fact that noise made the visual input barely
perceptible. Further, in Experiment 1, which did not involve background
noise, participants not only relied on both modalities, but generally
weighted these modalities according to the predictions of the optimal
model, that is, according to their relative reliability. At the
individual level, however, we found evidence of a between-subject
variation: Some participants relied more on the visual modality, whereas
others relied more on the auditory modality.

>>>>

Although the paradigm is within-subjects, we did not have enough
statistical power to fit a different model for each individual
participant (but see Experiment 4). Instead, models were constructed
with data collapsed across all participants. The fit was done with a
nonlinear least squares regression using the NLS package in R (Bates \&
Watts, 1988). We computed the values of the parameters, as well as their
95\% confidence intervals, through non-parametric bootstrap (using 10000
iterations).

\begin{table}

\caption{\label{tab:param}Statistics for the dataset we used.}
\centering
\begin{tabular}[t]{>{\bfseries}lrrrrrrr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{2}{c}{Auditory} & \multicolumn{2}{c}{Visual} & \multicolumn{3}{c}{Bimodal} \\
\cmidrule(l{2pt}r{2pt}){2-3} \cmidrule(l{2pt}r{2pt}){4-5} \cmidrule(l{2pt}r{2pt}){6-8}
Experiment & b\textsubscript{A} & Var\textsubscript{A} & b\textsubscript{V} & Var\textsubscript{V} & b\textsubscript{b} & Var\textsubscript{Ab} & Var\textsubscript{Vb}\\
\midrule
Experiment1 & 0.20 & 2.04 & 0.12 & 3.33 & 0.34 & 4.96 & 7.06\\
Experiment2 & 0.18 & 4.70 & 0.24 & 3.93 & 0.38 & 9.84 & 5.21\\
Experiment3 & 0.24 & 1.94 & -0.11 & 13.00 & 0.35 & 3.00 & 39.42\\
Experiment4 & 0.40 & 1.92 & 0.22 & 3.24 & 0.42 & 4.17 & 7.28\\
\bottomrule
\end{tabular}
\end{table}

@@

Average categorization judgments and best fits are shown in Figure
\ref{fig:unimodal}. The categorization function of the auditory
condition was slightly steeper than that of the visual condition,
meaning that participants perceived the sound tokens slightly more
categorically and with higher certainty than they did with the visual
tokens. The unimodal models' estimates are shown in Table
\ref{tab:param}.

@@

Figure~\ref{fig:bimodal} compares the predictions of the normative
models against human responses. Remember that the normative models use
variance estimates from the unimodal conditions (where people see input
from only one modality) to predict data in the bimodal condition (where
people see input from both modalities). Figure \ref{fig:bimodal} shows
the models' predictions comapred to human data.

@@

In the descriptive model, all parameters are fit to human responses in
the bimodal condition. The prediction of this model are shown in Figure
\ref{fig:bimodal}. Note that the descriptive model explained almost all
the variance, which makes it a reasonble proxy for human real
performance in the bimodal condition. Thus, to determine the extent to
which human data deviated from optimality, we comapred the descriptive
and optimal models follwoing the procedure outlined above (section XX).

\begin{figure}[!h]
\includegraphics[width=\textwidth]{ms_files/figure-latex/bimodal-1} \caption{Human responses vs. Models' predictions in the bimodal condition across the three experiments. Each point represents data form a particular audio-visual matching (corresponding to an instance from the set of 5x5 possible matchings in the audio-visual space). Shape represents auditory distance from the target, and color represents visual distance from the target. Thus, each point is characterized by both  shape and color.}\label{fig:bimodal}
\end{figure}

\subsubsection{Analysis of optimality}\label{analysis-of-optimality}

We analyzed if the cue combination was performed in an optimal way, or
if there was a systematic preference for one modality when making
decisions in the bimodal condition. As explained above
(\ref{fig:subOptim}), modality preference can be characterized formally
as a deviation from the decision threshold predicted by the optimal
model. The results in Figure \ref{fig:bias} (top) show both the decision
threshold derived from the descriptive model (in black) and the decision
threshold predicted by the optimal model (in red). The deviation from
optimality is compared to two hypothetical cases of modality preference
(dotted lines). We found that the descriptive and optimal decision
thresholds were almost identical. Indeed, non-parametric resampling of
the data showed no evidence of a deviation from the optimal prediction
(Figure~\ref{fig:bias}, bottom).

@@

We found that the optimal model explained largely more variance than
what can be explained with the auditory or the visual models alone. in
addition, the high correlation with the mean human data suggests that
the population was, overall, near-optimal. However, we see in Figure
\ref{fig:bimodal} that the responses deviated systematically from the
optimal prediction in that they were slightly pulled toward chance
(i.e., the probability 0.5). This fact is due to the increase in the
value of the variance associated with each modality (as can be noted
from Table \ref{tab:param}). Note however that, despite this increase in
randomness, our analysis of modality preference showed that the relative
values of these variances were not different (Figure~\ref{fig:bias}),
meaning that there was no evidence for a modality preference. Thus, 1)
There was a simultaneous increase in the values of the auditory and
visual variances in the bimodal condition compared to the unimodal
condition, meaning that the bimodal input lead to an increase in
response randomness, and 2) this increased randomness did not affect the
relative weighting of both modalities, i.e., the participants was
weighting modalities according to the relative reliability predicted by
the optimal model. This situation corresponds to the first case of
sub-optimality described in Figure~\ref{fig:subOptim}.

In Experiment 1, we tested word recognition when there was multimodal
uncertainty in terms of category membership and inherent perceptual
noise, only. In real life, however, both sound and visual tokens can
undergo distortions due to noisy factors in the environment (e.g., car
noise in the background, blurry vision in a foggy weather). In
Experiment 2 and 3, we explore this additional level of uncertainty.

@@

\subsection{Results}\label{results}

The analysis are similar to the analysis we did in Experiment 1.

\subsubsection{Unimodal condition}\label{unimodal-condition}

We fit a model for each modality. Figure \ref{fig:unimodal} shows human
responses together with their best fits. The visual data is a
replication of the visual data in Experiment 1. As for the auditory
data, in contrast to Experiment 1, responses were flatter, showing more
uncertainty.

We used the values derived from the unimodal condition (Table
\ref{tab:param}) to construct the visual, auditory and optimal models.
In addition, we fit a descriptive model which allows us to assess real
human performance in this condition. Figure~\ref{fig:bimodal} compares
the predictions of these models to human responses. Note that, in
contrast to Experiment 1, the visual model explained more variance than
the auditory model did.

\subsubsection{Analysis of optimality}\label{analysis-of-optimality-1}

We found, similar to Experiment 1, that the optimal model explained more
variance than the auditory or the visual models alone (Discuss the high
correlation, and why this not in itself a necessary but not sufficient
indicator of optimality). We also found a similar discrepancy between
the descriptive and optimal models as precision dropped for both the
auditory and the visual modalities. As for the weighting scheme used by
participants, contrary to Experiment 1 where modalities were weighted
according to their relative reliability, we found in this experiment
that the visual modality had a greater weight than what was expected
from its relative reliability. This situation corresponds to the second
case of sub-optimality described in Figure \ref{fig:subOptim}.

For the auditory modality, our parameter estimates were. For the visual
modality. Figure~\ref{fig:unimodal} shows responses in the unimodal
conditions as well as the corresponding fits. The auditory data is a
replication of the auditory data in Experiment 1. As for the visual
data, we found that, in contrast to Experiment 1 and 2, responses were
flatter, showing much more uncertainty.

Figure~\ref{fig:bimodal} compares the predictions of the visual,
auditory and optimal models to human responses. \#\#\#\# Descriptive
model Cross-validation using half the responses to predict the other
half yielded \(r^2=\)

We found that the optimal model accounted for almost all the variance.
However, whereas in previous experiments the optimal model explained
more variance than the auditory or the visual models, here the auditory
model explained at least as much variance. Thus, though participants
were still sensitive to variation in the noisy visual data in the
unimodal condition, they tended to ignore this information in the
bimodal condition, and relied almost exclusively on the non-noisy
auditory modality. The reason why we saw this (floor) effect when we
added noise to the visual modality (Experiment 3), and not when we added
noise to the auditory modality (Experiment 2), is the fact that our
visual stimuli were originally perceived less categorically and with
less certainty than the auditory stimuli. This fact made it more likely
for the visual categorization function to become flat and uninformative
after a few drops in precision due to noise on the one had, and to the
additional randomness induced by the bimodal presentation on the other
hand.

The past three experiments studied the problem of cue combination at the
population level --- The models were fit to the data aggregted across
all participants. However, optimality at the population level could be
misleading. Imagine, for instance, that in the bimodal condition half
the participants relied exclusively on the visual modality, whereas the
other half relied exclusively on the auditory modality. This case could
still lead to an aggregate behavior which appears optimal, but this
optimality would be spurious. Thus, we need to test cue integration at
the individual level as well. As we noted earlier, in previous
experiments we did not have enough statistical power to fit a different
model for each participant. In Experiment 4, below, we re-ran Experiment
1 (where we found near optimal behavior at the population level) while
extending its length, allowing us to collect the number of datapoints
necessary to fit the models for each participant.

\section{Experiment 4}\label{experiment-4}

\begin{figure}[htbp]
\centering
\includegraphics{ms_files/figure-latex/weights-1.pdf}
\caption{}
\end{figure}

@@

\subsection{Results}\label{results-1}

We fit both population-level models to the aggregated data (as in
Experiment 1), and individual models to data from each participant. For
the populaton-level models, the results are shown in Figure
\ref{fig:unimodal}, Figure \ref{fig:bimodal}, and Table \ref{tab:param}.
We note that the results mirrors the patterns obtained in Experiment 1.

At the individual level, we computed the distribution of optimal
weighing relative to the fitted (i.e., descriptive) weighing and we show
this distribution in Figure \ref{fig:weights}. The distribution centers
around the optimal prediction (i.e., 1) with a median value of XX
{[}XX,XX{]}. The variance of the distribution indicates that, while most
participants were near optimal in their cue combination, part of the
participant tended to rely predominantly on the auditory modality and
another part tended to rely predominantly on the visual modality.

@@

@@

In all of our experiments, at the highest level, we found generally
optimal behavior. Quantitatively speaking, the optimal model accounted,
respectively, for xx, xx, and xx of the variance in mean responses. When
compared to the predictions of the visual or the auditory models,
participants generally relied on both modalities to make their decisions
in the bimodal condition. Indeed, in Experiment 1 and 2, the optimal
model accounted for more variance in mean responses than the auditory or
the visual models did. In Experiment 3, participants appeared to rely on
one modality, but this was likely a floor effect, due to the fact that
noise made the visual input barely perceptible. Further, in Experiment
1, which did not involve background noise, participants not only relied
on both modalities, but generally weighted these modalities according to
the predictions of the optimal model, that is, according to their
relative reliability. At the individual level, however, we found
evidence of a between-subject variation: Some participants relied more
on the visual modality, whereas others relied more on the auditory
modality.
